---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r setup, include=FALSE}
library(dplyr)
library(ggplot2)
Sys.setlocale("LC_TIME", "English")
knitr::opts_chunk$set(echo = TRUE, fig.width = 10)
```

First load the data we need to analyze.  

```{r load}
  
  act<-read.csv("activity.csv")
```


## What is mean total number of steps taken per day?


```{r plot}
  total_steps<-with(act, tapply(steps,date,sum,na.rm=T))
  t<-data.frame(date=names(total_steps), steps=total_steps)
  g<-ggplot(t)
  print(g+geom_histogram(aes(steps,fill=date),binwidth = 400))
  print(mean(t$steps))
  print(median(t$steps))
```


## What is the average daily activity pattern?
And caculate the total number of steps per day:  

What is the average daily activity pattern?  

```{r plot2 }
  avg<-with(act,tapply(steps,interval, sum,na.rm=T))
  plot(names(avg),avg, type="l")
  abline(v=names(avg)[which.max(avg)],col="red")
  print(names(avg)[which.max(avg)])
```


## Imputing missing values

Imputing missing values:

```{r}
na<-sum(is.na(act))
```
The number of NA is `r na`.

Use mean to substitute NAs:  
```{r}
  act1<-act
  avg_mean = with(act,tapply(steps,interval,mean,na.rm=T))
  for(i in which(is.na(act))){
      act$steps[i]<-avg_mean[as.numeric(names(avg_mean))==act$interval[i]]
  }
```

Let's do the thing like before to see if there is any different:  
```{r}
  total_steps<-with(act, tapply(steps,date,sum,na.rm=T))
  t<-data.frame(date=names(total_steps), steps=total_steps)
  g<-ggplot(t)
  print(g+geom_histogram(aes(steps,fill=date),binwidth = 400))
  print(mean(t$steps))
  print(median(t$steps))
```


## Are there differences in activity patterns between weekdays and weekends?
```{r}
 
  act$weekdays <- strptime(act$date,"%Y-%m-%d")%>%format("%u")%>%as.numeric
  act$weekdays[act$weekdays %in% c(1,2,3,4,5)] = "weekday"
  act$weekdays[act$weekdays %in% c(6,7)] = "weekend"
  ggplot(act)+geom_line(aes(interval,steps,col=weekdays),alpha=0.8)+facet_grid(.~weekdays)
```






